SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-04-02 sedona-ieice16/final/reviews/review_response.tex

However, I have a question how to estimate each daemon's influence as time.
The estimation is important for accuracy of your proposed method.

For acceptance, please clarify the estimation method and its validity.

}

If I interpret your question correctly,
(1)~the identification process of infrequent, long-running daemons 
and (2)~the proposed {\em cutoff} method address your question. 
The cutoff is used as a criterion to determine whether to discard a sample, to improve measurement quality. 
Both are elaborated from Steps~2 through~9 in Figure~3, augmented with a one-line comment (above Step~2), 
for better clarification.

%Here is the summary of how to estimate each daemon's influence as time via the cutoffs. 
To estimate each daemon's influence, we do the following. 
\begin{itemize}
\item We run a program-under-test with 128 seconds, termed PUT128, 800 times 
enough to experience an infrequent, long-running daemon 
that may run every few hours or even once a day (Step~2).

\item From the 800 samples, we render a scatter-plot of pairs of successive samples of elapsed time (ET) of PUT128
as illustrated in Fig.~4~(b) and see if that scatter-plot has an $L$-shape (Step~3).

\item We check if the central cluster emerges (Step~4) by zooming into the scatter-plot (Step~4).

\item For each daemon in the central cluster, we compute the maximum and standard deviation 
of the process time (PT) of that daemon (Step~5). (As specified in the Characteristics paragraph, PT is defined as 
the sum of user and system time, supplied from the kernel via the Netlink interface, before and after each run.)

\item (1)~We identify, for each daemon in the samples in the $L$-shape (or $L$-sample), 
which daemon has its PT greater than two standard deviations above the maximum PT 
of that daemon. (2)~We also collect some extra processes (e.g. {\tt bash}, {\tt rhn\_check}) 
that are not in the cluster but only in the $L$-sample (Step~6). 
The identified processes are treated as infrequent, long-running.

\item For each so-identified infrequent, long-running daemon, we compute the minimum time 
in the $L$-samples (Step~7). (This computation provides the valley between the maximum PT from 
the central cluster and the minimum PT from the $L$-shape.)

\item We repeat Steps 2---6 with the much-longer running of PUT16384, to confirm if 
any of the identified daemons is actually not infrequent at the much larger task length of 16384 seconds (Step~8).
This step is required to prevent the false positive case in our identification process, 
as some daemons with a periodicity of hours are infrequent for a ``short'' program time like 128 seconds.

\item We now compute the {\em cutoff} for each of those identified infrequent, long-running daemons, 
based on the PUT128 and PUT16384 runs. 
\end{itemize}

%(The user- and system-time measures of captured processes are supplied by the kernel, via the Netlink interface.)

### 2017-04-02 sedona-ieice16/final/reviews/review_response.tex

However, I have a question how to estimate each daemon's influence as time.
The estimation is important for accuracy of your proposed method.

For acceptance, please clarify the estimation method and its validity.

}

If I understand your question right, 
we actually *measure* each daemon's process time (PT) for each run of a program-under-test, 
rather than estimate its influence as time. 
PT is computed based on the measures of user and system time received from the kernel via 
the Netlink socket.

To see whether the ``influence" (in your term) was significant on the timing, 
using the PT data we first identify infrequent, long-running daemons and then compute the *cutoff* of each so-identified daemon. 
As exhibited in Table~1, we obtain the detailed cutoff information for our identified infrequent, long-running daemon. 
The computed cutoffs are used to determine whether to discard a sample involving 
a daemon whose PT is above the respective cutoff, meaning that such a daemon's significant influence was there. 
The identification and cutoff computation are described from Steps~2 through~9, marked in blue, in Figure~3. 
For more details, please see the prose in Section~2 marked in blue.

The validity of our protocol using the cutoff was assessed on real-world programs and the SPEC CPU benchmark. 
As shown in Figure~5 and Table~3, we could obtain better measurement quality for those real workloads, compared to 
the existing timing scheme using elapsed time.

Note that to address your question, 
I slightly modified the Contribution paragraph for better clarification, and provided 
a single-line comment for better understanding about the cutoff computation.

If I didn't catch your question correctly, please kindly let me know so that I will re-address it.

### 2017-04-03 sedona-ieice16/final/reviews/review_response.tex

However, I have a question how to estimate each daemon's influence as time.
The estimation is important for accuracy of your proposed method.

For acceptance, please clarify the estimation method and its validity.

}

If I understand your question right, 
we actually *measure* each daemon's process time (PT) for each timing (sample) of a program-under-test, 
rather than estimate the influence of that daemon as time. 
Remind that PT is computed based on the measures of user and system time received from the kernel via 
the Netlink socket. To check whether the influence (in your terminology) was significant on each sample, 
we came up with an idea of the {\em cutoff} method by 
which we could eliminate a certain sample containing a daemon that ran over the respective cutoff time.

To determine the cutoff associated with each daemon, we first identify infrequent, long-running daemons (\hbox{Steps~2---8}). 
We then compute the cutoff of each so-identified daemon (Step~9). 
The detailed cutoff computation is specified in the second paragraph in the right column on page~3. 
The final cutoff data that we obtained for our identified daemon are exhibited in Table~1. 
For more details about the identification and cutoff calculation, please revisit the blue text in Section~2.

We applied the table to discard a sample involving 
a daemon whose PT is above the respective cutoff. Dropping a certain sample means that there happened such a daemon's significant influence on that sample. 
This indicates that we can't trust and include that sample in the base data to calculate the execution time of the given program.

The validity of our protocol using the cutoff was assessed on real-world programs (sort and matrix multiplication) and the SPEC CPU2006 benchmark. 
As shown in Figure~5 and Table~3, our protocol obtained better measurement quality 
for those real workloads, compared with that of the existing timing scheme using elapsed time.

For better clarification (to resolve your question), I slightly modified the Contribution paragraph, 
provided a single-line comment about the cutoff computation, and finally 
added the last sentence in parentheses in the prose of Step~9. 
These changes are marked in green. (Due to a space limit, more text could not be inserted.)

I hope my response to your concern resolved your question. But if I misunderstood you, please kindly let me know. I will re-address.

### 2017-04-03 sedona-ieice16/final/paper.tex
Sedona revision
Updates on SEDONA
Some changes

{\color{blue}
%\item We present an algorithm to identify infrequent, long-running daemons impacting 
%the timing of a compute-bound program.
%
%\item We propose a more accurate and precise protocol based on the identification variance 
%variance for that program.

\item We present an algorithm to identify and eliminate such infrequent and long-running 
daemons.

@@

{\color{blue}
\tcc{{\scriptsize Steps 2---9 produce cutoffs for each identified daemon.}}
\STATE Step 2. Perform a single PUT run (specifically, PUT128) for many samples (specifically, 800).
\STATE Step 3. Consider each pair of elapsed time measurements to be a dual-PUT measurement 
and examine a scatter-plot to see if it it displays an $L$-shape.
\STATE Step 4. Zoom into the central cluster to ensure that it is symmetric (roughly circular).
\STATE Step 5. Compute the maximum and standard deviation of the process time 
for each daemon encountered within the central cluster samples.
\STATE Step 6. Identify for each sample in the $L$-shape infrequent, long-running daemon executions. 
\STATE Step 7. Determine potentially periodic daemons based on the $L$-executions 
and for each daemon compute the minimum process time from those executions identified. 
\STATE Step 8. Perform Steps 1--6 above for a single run 
consisting of a small number of executions (specifically, 40) of PUT16384.  
\STATE Step 9. Compute the cutoffs for each identified daemon. 
}
\STATE Step 10. Discard an execution including a daemon of which process time is greater than the respective cutoff time.
\end{algorithmic}
\end{center}
\caption{Summary of the SEDONA Timing Protocol\label{alg:find}}
\vspace{-0.25in}
\end{figure}

{\bf A Running Example.} 
First, we set up the same measurement environment as described earlier in \hbox{Section}~\ref{sec:intro}, 
to eliminate known timing factors (Step~1).

{\color{blue}
We then run a program-under-test (called PUT) of 
Fig.~\ref{alg:put} with a task length of 128~sec, 
termed {\em PUT128}, 800 times (Step 2). 
(We render Fig.~\ref{fig:hist_before_et} using the 800 samples from this run.)
We use 128 seconds because that is long enough to perhaps experience an infrequent daemon. 
We run it 800 times to capture infrequent daemons that perhaps run every few hours or even 
once a day. 
Note that we collect all daemon processes as well as the PUT and their measures 
through the Netlink interface from the kernel before and after each 
timing.

@@

In Step~9 we compute 
the cutoff for each of those infrequent, long-running daemons so
identified, based on the runs of PUT128 and 
PUT16384 as collected in Tab.~\ref{tab:final_infrequent_cutoff}. 
Here is how to compute the cutoff. For the cutoff of such a daemon with PUT128, 
we take the \hbox{midpoint} between the maximum of that daemon's PTs in the 
central cluster (or 0, if absent) and the \hbox{minimum} of those in the $L$-samples. 
For the cutoff of such a daemon with PUT16384, we do the same. 
We then compute a ``task time'' as 5\% of the inferred periodicity. 
This 5\% ensures that such infrequent daemons will impact 
only a small percentage of the shorter PUTs, while presumably being 
associated with much larger cutoffs for the very long PUTs. 
We also include daemons that (a)~were identified as infrequent and 
\hbox{long-running} from PUT128 and (b)~were not identified as so in the PUT16384 
\hbox{$L$-samples}, but may have in the \hbox{dual-PUT32768} central cluster.
We then take the {\em maximum} of the two cutoffs for the final cutoff PT 
(the last column of Tab.~\ref{tab:final_infrequent_cutoff}). 
}

\vspace{-0.2in}
\begin{table}[ht]
\centering
{\tiny
\begin{tabular}{|p{1.2cm}|c|c|p{1cm}|p{1.45cm}|} \hline
{\tiny Process}  & {\tiny Cutoff PT} & {\tiny Cutoff PT} & {\tiny Task}  & {\tiny{\bf Final }} \\
{\tiny Name} & {\tiny on PUT128}  & {\tiny on PUT16K} & {\tiny Time} & {\tiny {\bf Cutoff PT}} \\\hline
{\tt bash} & 1 msec & --- & --- & {\bf 1 msec} \\ \hline
{\tt flush-9:0} & 64 msec & --- & $< 1$ hour & {\bf 64 msec} \\
                & ---     & 48 msec & $\geq 1$ hour & {\bf 48 msec} \\ \hline
{\tt grep }     & 1 msec & 12 msec & --- & {\bf 12 msec}\\ \hline
{\tt jbd2/md0-8} & 4 msec & --- & $< 1$ hour & {\bf 4 msec} \\
                & ---     & 11 msec & $\geq 1$ hour & {\bf 11 msec} \\ \hline
{\tt md0\_raid1} & 35 msec & ---     & $< 1$ hour  & {\bf 35 msec}\\
                 & ---     & 51 msec & $\geq 1$ hour & {\bf 51 msec} \\ \hline
{\tt rhn\_check}  & 281 msec & --- & $< 12$ min & {\bf 281 msec} \\
                 &  --- & 12,828 msec & $\geq 12$ min & {\bf 12,828 msec}\\ \hline
{\tt rhnsd} & 2 msec & --- & $< 12$ min & {\bf 2 msec} \\
            & ---    & 12 msec &$\geq 12$ min & {\bf 12 msec} \\ \hline
{\tt rhsmcertd}  & 1 msec & 1 msec & --- & {\bf 1 msec} \\  \hline
{\tt rhsmcertd}  & 57 msec & --- & $< 12$ min & {\bf 57 msec} \\
{\tt -worke}           &  --- & 119 msec  & $\geq 12$ min & {\bf 119 msec}\\ \hline
{\tt sshd} & 2 msec & 23 msec & --- & {\bf 23 msec}\\ \hline
\end{tabular}
}
\caption{Collected Infrequent, Long-running Daemons and Their Final Cutoff
  Process Time \hbox{(Step~9)}\label{tab:final_infrequent_cutoff}}
  \vspace{-0.3in}
\end{table}

@@

%\vspace{-0.in}
\begin{table}[t]
\centering
{
\tiny
\begin{tabular}{|p{0.1cm}|R{1.1cm}|R{1.1cm}|R{0.6cm}|R{0.6cm}|R{0.92cm}|R{0.92cm}|} \hline
 		  & \multicolumn{2}{c|}{{\tiny Execution Time (ms)}} & \multicolumn{2}{c|}{{\tiny Standard}}   & \multicolumn{2}{c|}{\multirow{2}{*}{{\tiny Relative Error}}}\\ \cline{2-3}
 & \multicolumn{1}{c|}{{\tiny{ORG}}}  & \multicolumn{1}{c|}{{\tiny{SED.}}} & \multicolumn{2}{c|}{{\tiny Deviation (ms)}}  & \multicolumn{2}{c|}{{\tiny}}\\ \cline{4-7}	
 & \multicolumn{1}{c|}{{\tiny{(in ET)}}} & \multicolumn{1}{c|}{{\tiny{(in PT)}}} & {\tiny{ORG}} & {\tiny{SED.}} & \multicolumn{1}{c|}{{\tiny{ORG}}}& \multicolumn{1}{c|}{{\tiny{SED.}}}\\ \hline
{{\tt 400}} & 454 & 445 & {3} & {2} & {6$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 401}} & 536,639 & 528,517 & {1,185} & {1,161} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 403}} & 26,109	& 25,695 & {138} & {96} & {5$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 410}} & 7,938 & 7,801 & {46} & {19} & {6$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 416}} & 1,015,342 & 999,846 & {965} & {876} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\%% V
{{\tt 429}} & 235,811 & 232,209 & {623} & {600} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 433}} & 480,586 & 473,256  & {743} & {725} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ %% V
{{\tt 434}} & 16,495  & 16,242  & {75} & {7} & {5$\times$10$^{-3}$} & {5$\times$10$^{-4}$}\\
{{\tt 435}} & 990,575 & 975,445  & {947} & {900} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
{{\tt 436}} & 1,160,742 & 1,143,078   & {3,914} & {3,843} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 437}} & 581,635 & 572,775 & {1,492} & {1,475}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 444}} & 591,201 & 582,229 & {294} & {281}  & {5$\times$10$^{-4}$} & {5$\times$10$^{-4}$}\\
{{\tt 445}} & 84,435  & 83,164  & {91} & {28}  & {1$\times$10$^{-3}$} & {3$\times$10$^{-4}$}\\
{{\tt 447}} & 521,846 & 513,493  & {150} & {108}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 450}} & 341,030 & 335,848  & {99} & {91}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 453}} & 258,797 & 254,496  & {623} & {582}  & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 454}} & 1,721,804 & 1,695,613  & {678} & {627}  & {4$\times$10$^{-4}$} & {4$\times$10$^{-4}$}\\
{{\tt 456}} & 410,533 & 404,328  & {85} & {50}  & {2$\times$10$^{-4}$} & {1$\times$10$^{-4}$}\\
{{\tt 458}} & 589,541 & 580,591  & {542} & {513} &  {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 459}} & 798,917 & 786,726  & {2,143} & {2,132}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 462}} & 595,188 & 586,120  & {3,326} & {3,274}  & {6$\times$10$^{-3}$} & {6$\times$10$^{-3}$}\\
{{\tt 464}} & 649,838 & 639,939  & {601} & {563}  & {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 465}} & 895,754 & 882,106  & {883} & {797}  & {1$\times$10$^{-3}$} & {1$\times$10$^{-3}$}\\
{{\tt 470}}	& 349,830 & 344,510 & {143} & {94} & {4$\times$10$^{-4}$} & {3$\times$10$^{-4}$}\\
{{\tt 471}} & 367,589 & 361,959  & {2,114} & {2,072} & {6$\times$10$^{-4}$} & {6$\times$10$^{-4}$}\\
{{\tt 473}} & 362,587 & 357,090  & {359} & {317} &  {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
%{{\tt 481}} & \multicolumn{4}{c}{Runtime Error}\\
{{\tt 482}} & 654,208	 & 644,223  & {2,436} & {2,392} &   {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\ %% V
%{{\tt 483}} & \multicolumn{4}{c}{Out-of-Scope}\\
{{\tt 998}} & 128	 & 127  & {0.6} & {0.6} &  {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 999}} & 128 &  127 & {0.8} & {0.6} &  {6$\times$10$^{-3}$} & {5$\times$10$^{-3}$}\\ \hline 
\multicolumn{3}{|r|}{Averages} & 852 & 815 &  {3$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ \hline
\end{tabular}
}
\caption{Performance Evaluation on the SPEC Benchmarks\label{tab:spec_real}}
\vspace{-0.25in}
\end{table}

@@

\vspace{-0.03in}
{\tiny 
\bibliographystyle{ieicetr} 
\bibliography{paper}
%\vspace{-0.2in}
}

>>>>

{\color{green}
%\item We present an algorithm to identify infrequent, long-running daemons impacting 
%the timing of a compute-bound program.
%
%\item We propose a more accurate and precise protocol based on the identification variance 
%variance for that program.

\item We present an algorithm to identify and eliminate such daemons that are infrequent, long-running.

@@

{\color{blue}
\tcc{{\color{green}{\scriptsize Daemon-cutoff times are derived from Steps~2 through~9.}}}
\STATE Step 2. Perform a single PUT run (specifically, PUT128) for many samples (specifically, 800).
\STATE Step 3. Consider each pair of elapsed time measurements to be a dual-PUT measurement 
and examine a scatter-plot to see if it it displays an $L$-shape.
\STATE Step 4. Zoom into the central cluster to ensure that it is symmetric (roughly circular).
\STATE Step 5. Compute the maximum and standard deviation of the process time 
for each daemon encountered within the central cluster samples.
\STATE Step 6. Identify for each sample in the $L$-shape infrequent, long-running daemon executions. 
\STATE Step 7. Determine potentially periodic daemons based on the $L$-executions 
and for each daemon compute the minimum process time from those executions identified. 
\STATE Step 8. Perform Steps 1--6 above for a single run 
consisting of a small number of executions (specifically, 40) of PUT16384.  
\STATE Step 9. Compute the cutoffs for each identified daemon. 
}
\STATE Step 10. Discard an execution including a daemon of which process time is greater than the respective cutoff time.
\end{algorithmic}
\end{center}
\caption{Summary of the SEDONA Timing Protocol\label{alg:find}}
\vspace{-0.25in}
\end{figure}

{\bf A Running Example.} 
First, we set up the same measurement environment as described earlier in \hbox{Section}~\ref{sec:intro}, 
to eliminate known timing factors (Step~1).
{\color{blue}
We then run a program-under-test (called PUT) of 
Fig.~\ref{alg:put} with a task length of 128~sec, 
termed {\em PUT128}, 800 times (Step 2). 
(We render Fig.~\ref{fig:hist_before_et} using the 800 samples from this run.)
We use 128 seconds because that is long enough to perhaps experience an infrequent daemon. 
We run it 800 times to capture infrequent daemons that perhaps run every few hours or even 
once a day. 
Note that we collect all daemon processes as well as the PUT and their measures 
through the Netlink interface from the kernel before and after each 
timing.

@@

In Step~9 we compute 
the cutoff for each of those infrequent, long-running daemons so
identified, based on the runs of PUT128 and 
PUT16384 as collected in Tab.~\ref{tab:final_infrequent_cutoff}. 
Here is how to compute the cutoff. For the cutoff of such a daemon with PUT128, 
we take the \hbox{midpoint} between the maximum of that daemon's PTs in the 
central cluster (or 0, if absent) and the \hbox{minimum} of those in the $L$-samples. 
For the cutoff of such a daemon with PUT16384, we do the same. 
We then compute a ``task time'' as 5\% of the inferred periodicity. 
This 5\% ensures that such infrequent daemons will impact 
only a small percentage of the shorter PUTs, while presumably being 
associated with much larger cutoffs for the very long PUTs. 
We also include daemons that (a)~were identified as infrequent and 
\hbox{long-running} from PUT128 and (b)~were not identified as so in the PUT16384 
\hbox{$L$-samples}, but may have in the \hbox{dual-PUT32768} central cluster.
We then take the {\em maximum} of the two cutoffs for the final cutoff PT 
(the last column of Tab.~\ref{tab:final_infrequent_cutoff}). 
({\color{green}Note that different cutoff data from Tab.~\ref{tab:final_infrequent_cutoff} may be yielded on a different kernel.})
}

\vspace{-0.3in}
\begin{table}[ht]
\centering
{\tiny
\begin{tabular}{|p{1.2cm}|c|c|p{1cm}|p{1.45cm}|} \hline
{\tiny Process}  & {\tiny Cutoff PT} & {\tiny Cutoff PT} & {\tiny Task}  & {\tiny{\bf Final }} \\
{\tiny Name} & {\tiny on PUT128}  & {\tiny on PUT16K} & {\tiny Time} & {\tiny {\bf Cutoff PT}} \\\hline
{\tt bash} & 1 msec & --- & --- & {\bf 1 msec} \\ \hline
{\tt flush-9:0} & 64 msec & --- & $< 1$ hour & {\bf 64 msec} \\
                & ---     & 48 msec & $\geq 1$ hour & {\bf 48 msec} \\ \hline
{\tt grep }     & 1 msec & 12 msec & --- & {\bf 12 msec}\\ \hline
{\tt jbd2/md0-8} & 4 msec & --- & $< 1$ hour & {\bf 4 msec} \\
                & ---     & 11 msec & $\geq 1$ hour & {\bf 11 msec} \\ \hline
{\tt md0\_raid1} & 35 msec & ---     & $< 1$ hour  & {\bf 35 msec}\\
                 & ---     & 51 msec & $\geq 1$ hour & {\bf 51 msec} \\ \hline
{\tt rhn\_check}  & 281 msec & --- & $< 12$ min & {\bf 281 msec} \\
                 &  --- & 12,828 msec & $\geq 12$ min & {\bf 12,828 msec}\\ \hline
{\tt rhnsd} & 2 msec & --- & $< 12$ min & {\bf 2 msec} \\
            & ---    & 12 msec &$\geq 12$ min & {\bf 12 msec} \\ \hline
{\tt rhsmcertd}  & 1 msec & 1 msec & --- & {\bf 1 msec} \\  \hline
{\tt rhsmcertd}  & 57 msec & --- & $< 12$ min & {\bf 57 msec} \\
{\tt -worke}           &  --- & 119 msec  & $\geq 12$ min & {\bf 119 msec}\\ \hline
{\tt sshd} & 2 msec & 23 msec & --- & {\bf 23 msec}\\ \hline
\end{tabular}
}
\caption{Collected Infrequent, Long-running Daemons and Their Final Cutoff
  Process Time \hbox{(Step~9)}\label{tab:final_infrequent_cutoff}}
  \vspace{-0.3in}
\end{table}

@@

\vspace{-0.in}
\begin{table}[t]
\centering
{
\tiny
\begin{tabular}{|p{0.1cm}|R{1.1cm}|R{1.1cm}|R{0.6cm}|R{0.6cm}|R{0.92cm}|R{0.92cm}|} \hline
 		  & \multicolumn{2}{c|}{{\tiny Execution Time (ms)}} & \multicolumn{2}{c|}{{\tiny Standard}}   & \multicolumn{2}{c|}{\multirow{2}{*}{{\tiny Relative Error}}}\\ \cline{2-3}
 & \multicolumn{1}{c|}{{\tiny{ORG}}}  & \multicolumn{1}{c|}{{\tiny{SED.}}} & \multicolumn{2}{c|}{{\tiny Deviation (ms)}}  & \multicolumn{2}{c|}{{\tiny}}\\ \cline{4-7}	
 & \multicolumn{1}{c|}{{\tiny{(in ET)}}} & \multicolumn{1}{c|}{{\tiny{(in PT)}}} & {\tiny{ORG}} & {\tiny{SED.}} & \multicolumn{1}{c|}{{\tiny{ORG}}}& \multicolumn{1}{c|}{{\tiny{SED.}}}\\ \hline
{{\tt 400}} & 454 & 445 & {3} & {2} & {6$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 401}} & 536,639 & 528,517 & {1,185} & {1,161} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 403}} & 26,109	& 25,695 & {138} & {96} & {5$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 410}} & 7,938 & 7,801 & {46} & {19} & {6$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 416}} & 1,015,342 & 999,846 & {965} & {876} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\%% V
{{\tt 429}} & 235,811 & 232,209 & {623} & {600} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 433}} & 480,586 & 473,256  & {743} & {725} & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ %% V
{{\tt 434}} & 16,495  & 16,242  & {75} & {7} & {5$\times$10$^{-3}$} & {5$\times$10$^{-4}$}\\
{{\tt 435}} & 990,575 & 975,445  & {947} & {900} & {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
{{\tt 436}} & 1,160,742 & 1,143,078   & {3,914} & {3,843} & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 437}} & 581,635 & 572,775 & {1,492} & {1,475}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 444}} & 591,201 & 582,229 & {294} & {281}  & {5$\times$10$^{-4}$} & {5$\times$10$^{-4}$}\\
{{\tt 445}} & 84,435  & 83,164  & {91} & {28}  & {1$\times$10$^{-3}$} & {3$\times$10$^{-4}$}\\
{{\tt 447}} & 521,846 & 513,493  & {150} & {108}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 450}} & 341,030 & 335,848  & {99} & {91}  & {3$\times$10$^{-4}$} & {2$\times$10$^{-4}$}\\
{{\tt 453}} & 258,797 & 254,496  & {623} & {582}  & {2$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\
{{\tt 454}} & 1,721,804 & 1,695,613  & {678} & {627}  & {4$\times$10$^{-4}$} & {4$\times$10$^{-4}$}\\
{{\tt 456}} & 410,533 & 404,328  & {85} & {50}  & {2$\times$10$^{-4}$} & {1$\times$10$^{-4}$}\\
{{\tt 458}} & 589,541 & 580,591  & {542} & {513} &  {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 459}} & 798,917 & 786,726  & {2,143} & {2,132}  & {3$\times$10$^{-3}$} & {3$\times$10$^{-3}$}\\
{{\tt 462}} & 595,188 & 586,120  & {3,326} & {3,274}  & {6$\times$10$^{-3}$} & {6$\times$10$^{-3}$}\\
{{\tt 464}} & 649,838 & 639,939  & {601} & {563}  & {9$\times$10$^{-4}$} & {9$\times$10$^{-4}$}\\
{{\tt 465}} & 895,754 & 882,106  & {883} & {797}  & {1$\times$10$^{-3}$} & {1$\times$10$^{-3}$}\\
{{\tt 470}}	& 349,830 & 344,510 & {143} & {94} & {4$\times$10$^{-4}$} & {3$\times$10$^{-4}$}\\
{{\tt 471}} & 367,589 & 361,959  & {2,114} & {2,072} & {6$\times$10$^{-4}$} & {6$\times$10$^{-4}$}\\
{{\tt 473}} & 362,587 & 357,090  & {359} & {317} &  {1$\times$10$^{-3}$} & {9$\times$10$^{-4}$}\\
%{{\tt 481}} & \multicolumn{4}{c}{Runtime Error}\\
{{\tt 482}} & 654,208	 & 644,223  & {2,436} & {2,392} &   {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\ %% V
%{{\tt 483}} & \multicolumn{4}{c}{Out-of-Scope}\\
{{\tt 998}} & 128	 & 127  & {0.6} & {0.6} &  {4$\times$10$^{-3}$} & {4$\times$10$^{-3}$}\\
{{\tt 999}} & 128 &  127 & {0.8} & {0.6} &  {6$\times$10$^{-3}$} & {5$\times$10$^{-3}$}\\ \hline 
\multicolumn{3}{|r|}{Averages} & 852 & 815 &  {3$\times$10$^{-3}$} & {2$\times$10$^{-3}$}\\ \hline
\end{tabular}
}
\caption{Performance Evaluation on the SPEC Benchmarks\label{tab:spec_real}}
\vspace{-0.25in}
\end{table}

@@

{\tiny 
%\vspace{-0.05in}
\bibliographystyle{ieicetr} 
\bibliography{paper}
%\vspace{-0.2in}
}
